---
title: "classwork-Thurs-3-9.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("paleotree")
install.packages(“paleobioDB”)
#Then start a code block 
```

```{r}
library(paleobioDB)
library(paleotree)
# candids <- pdbd_occurences (limit="all", vocab = "pbdb", base_name= "Canidae", show=c )
data(graptPBDB)
ls()
head(graptOccPBDB)
```

#graptOccPBDB

occSpecies <- taxonSortPBDBocc(graptOccPBDB, rank="species")
#plot species occurences
plotOccData(occSpecies,groupLabel = "Species")
#convert occurance data to "timelist" format
graptTimeSpecies <- occData2timeList(occList=occSpecies)
#plot diveristy through time
taxicDivDisc(graptTimeSpecies)

head(graptTimeSpecies)

head(occSpecies)
occGenera <- taxonSortPBDBocc(graptOccPBDB, rank="genus")
occGenera <- taxonSortPBDBocc(graptOccPBDB, rank=family")

taxicDivDisc(graptTimeSpecies)
taxicDivDisc(graptTimeGenus)
taxicDivDisc(graptTimeFamily)

pdf(file="dtt.pdf") #creates pdf 
taxicDivDisc(graptTimeSpecies)
taxicDivDisc(graptTimeGenus)
taxicDivDisc(graptTimeFamily)

```{r}

graptTimeSpecies <- occData2timeList(occList=occSpecies)
graptTimeGenus <- occData2timeList(occList=occGenus)
```

```{r}
library(forcats)

canid_occ <- ggplot(canids, aes( x - ))
#post this code after class
#make plots look like this 
```

ggsave("faceted-ranges.pdf" scale = 6)

#this code block can be used for data 

diversity <- canids %>% gather(key = type, value = age, minage, maxage)

head(diversity)

#plot it 
ggplot(diversity,aes(x = age, y = diversity)) + geom_step()